\documentclass{article}

  

\newcommand{\functiondefinition}[3]{Function:#1

Arguments:#2

Description: #3}
\begin{document}

\section{``{\tt Audio}'' class requirements}

Every class named Audio must have the following functions:

\functiondefinition{\_\_init\_\_}{}{Initialization that requires no arguments}
\functiondefinition{reset}{}{Function to set the state of the Audio object back to ``pristine".}
\functiondefinition{load\_data}{data:Raw sound data to load., format:The format of the sound data.}{A function to load raw sound data into an internal buffer, of some sort, for later playback}
\functiondefinition{record}{t:Time to start recording.}{}
\functiondefinition{is\_recording}{}{}
\functiondefinition{play}{}{Plays all sound data until stop() is called.  May block.}
\functiondefinition{play\_init}{}{Initializes playback of data.  Does not actually start playing back.  Use this before repeated calls to play\_tick()}
\functiondefinition{play\_tick}{ttpt:Time to play to.}{}
\functiondefinition{is\_playing}{}{}
\functiondefinition{get\_s\_played}{}{Gets the number of seconds played in the currently-playing sound.}
\functiondefinition{get\_time\_of\_first\_event}{}{Gets the time the first audio file starts.}
\functiondefinition{get\_current\_audio\_start\_time}{Gets the time the current audio file starts.}
\functiondefinition{pause}{}{Pauses playback/recording.}
\functiondefinition{unpause}{}{Unpauses playback/recording.}
\functiondefinition{stop}{}{Stops playback/recording.}

\section{``{\tt GUI} class requirements}

\section{``{\tt Canvas} class requirements}

\end{document}
